### 2024-04-22 parts/appendix.tex
moving fact to appendix

\begin{proofof}[derivation-monomials:fact]
    Let $M \defined X_1^{k_1} \cdots X_n^{k_n}$,
    where $k_1, \dots, k_n > 0$ and $n > 0$.
    Let us compute
    \begin{align*}
        \Diff{K}{M} &= \prod_{i = 1}^n X_i^{k_i} - \prod_{i = 1}^n (X_i - K)^{k_i} \\
                    &= \sum_{p = 1}^n \frac{K}{X_p - K} \prod_{i = 1}^n (X_i - K)^{k_i} 
    \end{align*}
    Therefore, 
    the \kl{maximal monomials} of $\Diff{K}{M}$
    are precisely
    of the form $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$ for some $1 \leq p \leq i$,
    which \kl{strictly divides} $M$.
    Let $T$ be a \kl{monomial} that \kl{strictly divides} $M$,
    then, $T = \prod_{i = 1}^n X_i^{t_i}$, 
    for all $1 \leq i \leq n$, $t_i \leq k_i$,
    and there exists $1 \leq p \leq n$ such that$ t_j < k_j$.
    In particular, $T$ \kl{divides}
    $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$.
\end{proofof}

>>>>

\begin{fact}
    \label{derivation-monomials:fact}
    Let $K > 0$,
    and let $M,T$ be two \kl{monomials}, such that
    $T$ \kl{strictly divides} $M$.
    Then,
    every \kl{monomial} of $\Diff{K}{M}$ \kl{strictly divides} $M$,
    and 
    $T$ \kl{divides} some \kl{maximal monomial}
    of $\Diff{K}{M}$, which has a coefficient
    that is a multiple of $K$.
    \proofref{derivation-monomials:fact}
\end{fact}
\begin{proofof}[derivation-monomials:fact]
    Let $M \defined X_1^{k_1} \cdots X_n^{k_n}$,
    where $k_1, \dots, k_n > 0$ and $n > 0$.
    Let us compute
    \begin{align*}
        \Diff{K}{M} &= \prod_{i = 1}^n X_i^{k_i} - \prod_{i = 1}^n (X_i - K)^{k_i} \\
                    &= \sum_{p = 1}^n \frac{K}{X_p - K} \prod_{i = 1}^n (X_i - K)^{k_i} 
    \end{align*}
    Therefore, 
    the \kl{maximal monomials} of $\Diff{K}{M}$
    are precisely
    of the form $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$ for some $1 \leq p \leq i$,
    which \kl{strictly divides} $M$.
    Let $T$ be a \kl{monomial} that \kl{strictly divides} $M$,
    then, $T = \prod_{i = 1}^n X_i^{t_i}$, 
    for all $1 \leq i \leq n$, $t_i \leq k_i$,
    and there exists $1 \leq p \leq n$ such that$ t_j < k_j$.
    In particular, $T$ \kl{divides}
    $K \frac{\prod_{i = 1}^n X_i^{k_i}}{X_p}$.
\end{proofof}
